Packaging research artefacts with RO-Crate

### 2022-01-01 latex/ro-crate.tex
PROV-O citation, ieee2791 permalink

This workflow run profile is a continuation of our previous work with
capturing workflow provenance in a Research Object in CWLProv
\cite{doi:10.1093/gigascience/giz095} and TavernaPROV
\cite{doi:10.5281/zenodo.51314}. In both cases, we used the PROV Ontology
\cite{CheckMyCrate}, including details of every task execution with all the
intermediate data, which required significant workflow engine
integration.\footnote{CWLProv and TavernaProv predate RO-Crate, but use
RO-Bundle\cite{doi:10.5281/zenodo.12586}, a similar Research Object
packaging method with JSON-LD metadata.}

@@

BioCompute Objects\footnote{\url{https://biocomputeobject.org/}} (BCO)
\cite{doi:10.1371/journal.pbio.3000099} is a community-led effort to
standardise submissions of computational workflows to biomedical
regulators. For instance, a genomics sequencing pipeline, as part of a
personalised cancer treatment study, can be submitted to the US Food
and Drugs Administration (FDA) for approval. BCOs are formalised in the
standard IEEE 2791-2020 \cite{doi:10.1109/IEEESTD.2020.9094416} as a
combination of JSON
Schemas\footnote{\url{https://opensource.ieee.org/2791-object/ieee-2791-schema/}}
that define the structure of JSON metadata files describing exemplar
workflow runs in detail, covering aspects such as the usability and
error domain of the workflow, its runtime requirements, the reference
datasets used and representative output data produced.

>>>>

This workflow run profile is a continuation of our previous work with
capturing workflow provenance in a Research Object in CWLProv
\cite{doi:10.1093/gigascience/giz095} and TavernaPROV
\cite{doi:10.5281/zenodo.51314}. In both cases, we used the PROV Ontology
\cite{PROVO}, including details of every task execution with all the
intermediate data, which required significant workflow engine
integration.\footnote{CWLProv and TavernaProv predate RO-Crate, but use
RO-Bundle\cite{doi:10.5281/zenodo.12586}, a similar Research Object
packaging method with JSON-LD metadata.}

@@

BioCompute Objects\footnote{\url{https://biocomputeobject.org/}} (BCO)
\cite{doi:10.1371/journal.pbio.3000099} is a community-led effort to
standardise submissions of computational workflows to biomedical
regulators. For instance, a genomics sequencing pipeline, as part of a
personalised cancer treatment study, can be submitted to the US Food
and Drugs Administration (FDA) for approval. BCOs are formalised in the
standard IEEE 2791-2020 \cite{doi:10.1109/IEEESTD.2020.9094416} as a
combination of JSON
Schemas\footnote{\url{https://w3id.org/ieee/ieee-2791-schema/}}
that define the structure of JSON metadata files describing exemplar
workflow runs in detail, covering aspects such as the usability and
error domain of the workflow, its runtime requirements, the reference
datasets used and representative output data produced.
